---
title: "WSDM FINAL MODEL AND PLOT"
author: "Adhi Perdana"
date: '2022-11-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Read The library

```{r}
library(tibble)
library('readr') 
library('data.table') 
library('tidyr')
library('stringr')
library('forcats')
library('lubridate')
library(dplyr)
library('ggplot2') # visualisation
library('scales') # visualisation
library('grid') # visualisation
library('gridExtra') # visualisation
library('RColorBrewer')# visualisation
library('corrplot')
library(plotly)
library(glue)
library(psych)
library(forcats)
library(stargazer)
library(caret)
library(gmodels)
library(BBmisc)
library(partykit)
library(lubridate)
library(psych)
library(rpart)
library(rattle)
library(rpart.plot)
library(caret)
library(GGally)
library(yardstick)
library(randomForest)
library(ggplot2)
library(hrbrthemes)
library(dplyr)
library(tidyr)
library(viridis)
library(scales)
```



```{r}
# Model Dataset
## Load the dataset for model

# df train
wsdm_finaldf_train <-readRDS("wsdm_finaldf_train.RDS")
# df test for decision tree
wsdm_finaldf_test <-readRDS("wsdm_finaldf_test.RDS")
# tuning model for logistic
wsdm_model2_test <-readRDS("wsdm_model2_test.RDS")
wsdm_model2_train <-readRDS("wsdm_model2_train.RDS")
# logistic Model
kkbox_logistic_model2 <- readRDS("kkbox_logistic_model2 .RDS")
summary(kkbox_logistic_model2)
```

#  Data Visualization
## Load the dataset for DV

```{r}
# For Listening hour
forest_viz_ggplot
#For loyalty and  churn
forest_viz_loyality
# For Registration line plot
wsdm_for_registration
# For auto renew
forest_viz_auto_renew_plot
```

## Data Visualization
```{r}
# For listening hour'
forest_dataviz_ggplot <-ggplot(forest_viz_ggplot, aes(fill=condition, y=listening_hour, x=value,text=paste0( "Churn or stay: ", condition, "<br>",
        "number of subscriber: ", scales::comma(value, 1), "<br>"))) + 
    geom_bar(position="stack", stat="identity") +
     scale_x_continuous(labels = scales::comma) +
    scale_fill_viridis(discrete = T) +
    ggtitle("churn by listening hour") +
      labs(x = 'Number of Subscriber',
       y = ' Listening Hours',
       title = 'Number of churned customer by listening hour')+
     theme_algoritma

ggplotly(forest_dataviz_ggplot, tooltip = "text")
```

Data Visualization Loyalty and churn
```{r}
forest_loyalty_scattter_tooltip <-ggplot(forest_viz_loyality, aes( x=loyality_range, y=churn,text=paste0("years :" ,loyality_range,"<br>",
        "number of churn: ", scales::comma(churn, 1),"<br>",
        "number of stay: ", scales::comma(stay, 1)))) + 
    geom_point(aes(color=loyality_range) ) +
     scale_x_continuous(labels = scales::comma) +
   scale_y_continuous(labels = scales::comma)  +
    ggtitle("churn by listening hour") +
      labs(x = 'year',
       y = ' Number of churn customer',
       title = 'Relationship between loyality and churn customer')+
    theme_algoritma
```

```{r}
ggplotly(forest_loyalty_scattter_tooltip, tooltip = "text")
```
Data Visualization to show the growth of subscriber
```{r pressure, echo=FALSE}
# registration plot
wsdm_for_registration_plot <- wsdm_for_registration  %>%
  head(14) %>%
  ggplot( aes(x=year_registration, y=`number of subscriber`)) +
    geom_line() +
    geom_point(color="#69b3a2", size=4) +
     scale_y_continuous(labels = scales::comma)  +
    ggtitle("Subscriber Growth year to year") +
    ylab("number of subscriber") +
    theme_ipsum()
```

Data Visualization to show the number of customer who use auto_renew features
```{r pressure, echo=FALSE}
# Auto renew plot
auto_renew_plot <-ggplot(forest_viz_auto_renew_plot, aes(fill=`churn or not`, y=`has auto renew feature?`, x=`number of subscriber`,text=paste0( "Churn or stay: ", `churn or not`, "<br>",
        "number of subscriber: ", scales::comma(`number of subscriber`, 1), "<br>"))) + 
    geom_bar(position="stack", stat="identity") +
     scale_x_continuous(labels = scales::comma) +
    scale_fill_viridis(discrete = T) +
    ggtitle("churn by auto renew feature") +
      labs(x = 'Number of Subscriber',
       y = ' have auto renew feature or not ?',
       title = 'Number of churned customer by auto renew feature')+
     theme_algoritma
ggplotly(auto_renew_plot, tooltip = "text")
```




# Model
## load Random Forest model
```{r}
# For Model
forest_model_lr <-readRDS("forest_model_lr.RDS")
# For variable importance plot
data_viz_varmp <- readRDS("data_viz_varmp.RDS")
# For variable importance df
varmp_lr_plotreadRDS('varmp_lr_plot.RDS')
```

```{r}
wsdm_forest_split_class_lr <- predict( forest_model_lr, forest_test_lr, type = "class")
wsdm_forest_split_prob_lr <- predict( forest_model_lr, forest_test_lr, type = "prob")
```

```{r}
wsdm_forest_pred_lr <-select(forest_test_lr, is_churn) %>%
  bind_cols(churn_pred = wsdm_forest_split_class_lr  ) %>% 
  bind_cols(stay_prob =  wsdm_forest_split_prob_lr[,1]) %>% 
   bind_cols(churn_prob = round(wsdm_forest_split_prob_lr [,2]))
```
```{r}
wsdm_forest_pred_lr $churn_pred<- ifelse(wsdm_forest_pred_lr $churn_pred ==1,"churn","stay")
wsdm_forest_pred_lr  $is_churn<- ifelse(wsdm_forest_pred_lr $is_churn ==1,"churn","stay")
wsdm_forest_pred_lr $churn_pred<- as.factor(wsdm_forest_pred_lr $churn_pred)
wsdm_forest_pred_lr $is_churn<- as.factor(wsdm_forest_pred_lr $is_churn)
```
```{r}
confmat_forest_model_lr <- wsdm_forest_pred_lr %>% 
  conf_mat(is_churn,churn_pred) %>% 
  autoplot(type = "heatmap")
```

```{r}
forest_model_evalmat_lr <-wsdm_forest_pred_lr %>%
  summarise(
    accuracy = accuracy_vec(is_churn, churn_pred),
    sensitivity = sens_vec(is_churn, churn_pred),
    specificity = spec_vec(is_churn, churn_pred),
    precision = precision_vec(is_churn, churn_pred)
  )
```
Variable importance Random forest 
```{r}
varmp_lr_dv <- ggplot(varmp_lr_plot, aes(x =`mean decrease gini` ,y = reorder(variable, `mean decrease gini`))) +
  geom_col(aes(fill = `mean decrease gini`), show.legend = F) +
  labs(title = "Variable importance in Random Forest Model",
       subtitle = "KKBOXX Online Music Streaming",
       x = "Variable importance",
       y = NULL) +
  geom_label(aes(label = comma(`mean decrease gini`)), hjust = 1.05) +
  scale_fill_gradient(low = "gray", high = "blue") +
  theme_minimal()
```
Variable importance Random forest with tooltip
```{r}
varimp_forest_plotly <-ggplot(data_viz_varmp, aes(x = `mean decrease gini`, y = reorder(variable, `mean decrease gini`))) +
  geom_col(aes(fill = `mean decrease gini`, text = tooltip)) +
  scale_fill_continuous(low = "gray", high = "blue") +
  guides(fill = FALSE) +
  labs(
    title = "Variable importance in Random Forest Model",
    subtitle = "KKBOXX Online Music Streaming",
    x = "variable importance",
    y = NULL
  ) +
  theme_minimal()
```
```{r}
ggplotly(varimp_forest_plotly, tooltip = "text")
```





